The Iterative Signature Algorithm

### 2009-08-06 isa2/inst/doc/ISA_tutorial.Rnw
Update vignettes, do not mess with sessionInfo() because the vignette fails if sessionInfo() to toLatex() output is changed.
isa2: put vignette images into subdir.

@@

<<blockplot.pre,echo=FALSE,results=hide>>=
png("blockplot.png", 800, 600)
@ 
<<blockplot>>=
images(list(data), xlab="", ylab="", strip=FALSE)
@ 
<<blockplot.post,echo=FALSE,results=hide>>=
dev.off()
@

@@

<<tenmods.pre,echo=FALSE,results=hide>>=
png("tenmods.png", 600, 400)
@ 
<<tenmods>>=
images(list(data[[1]]), strip=FALSE, xlab="", ylab="")
@ 
<<tenmods.post,echo=FALSE,results=hide>>=
dev.off()
@

@@

Finally, let us take a look at some of the other modules, that were
also kept after the robustness-based filtering. Here we plot five of
them, together with the input matrix.
<<othermods.pre,echo=FALSE,results=hide>>=
png("othermods.png", 400, 400)
@ 
<<othermods>>=
othermods <- order(modules3$seeddata$rob)[1:5]
print(plotModules(modules3, othermods, data=data[[1]]))
@ 
<<othermods.post,echo=FALSE,results=hide>>=
dev.off()
@

@@

The \Rfunction{drawHeatmap} function of the \Rpackage{biclust} package
can be also used to draw an image plot. This visualizes a single
bicluster on top of the input matrix. It reorders the rows and columns
of the input matrix to move the block of the bicluster to the top
left corner of the input matrix (Fig.~\ref{fig:heatmap}).
<<drawHeatmap.pre,echo=FALSE,results=hide>>=
png("drawheatmap.png", 400,400)
@ 
<<drawHeatmap>>=
drawHeatmap(five.mods[[1]], Bc, number=1,local=FALSE)
@ 
<<drawHeatmap.post,echo=FALSE,results=hide>>=
dev.off()
@ 
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{drawheatmap}
\caption{Heatmap plot of the reordered input matrix. The rows and
  columns corresponding to the first bicluster are moved to the
  top-left corner of the matrix.}
\label{fig:heatmap}
\end{figure}

@@

<<noiseplot.pre,echo=FALSE,results=hide>>=
png("noise.png", width=800, height=600)
@ 
<<noiseplot>>=
images(lapply(data, "[[", 1), names=as.character(noise), 
       xlab="", ylab="")
@ 
<<noiseplot.post,echo=FALSE,results=hide>>=
dev.off()
@ 
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{noise}
  \caption{Modular data sets with different levels of noise. The data
  sets are generated by adding normally distributed background noise
  with given variance to the checkerboard matrix.}
  \label{fig:noise}
\end{figure}

@@

<<overlapplot.pre,echo=FALSE,results=hide>>=
png("overlapplot.png", 800, 600)
@ 
<<overlapplot>>=
plotModules(data=two.over[[1]],
            list(rows=cbind(ov.modules.1$rows, ov.modules.2$rows),
                 columns=cbind(ov.modules.1$columns,
                   ov.modules.2$column)),
            names=c("Input matrix", paste("Module", 1:6)))
@
<<overlapplot.post,echo=FALSE,results=hide>>=
dev.off()
@

@@

<<sessioninfo,results=tex,echo=FALSE>>=
gsub(";", "; ", gsub("_", "\\\\_", sub("Locale:[ ]*\\\\verb\\|(.*)\\|", 
                                       "\\\\texttt\\{\\1\\}", 
                                       toLatex(sessionInfo()))))
@

>>>>

\SweaveOpts{prefix.string=graphics/plot}

@@

<<blockplot.pre,echo=FALSE,results=hide>>=
png("graphics/blockplot.png", 800, 600)
@ 
<<blockplot>>=
images(list(data), xlab="", ylab="", strip=FALSE)
@ 
<<blockplot.post,echo=FALSE,results=hide>>=
dev.off()
@

@@

<<tenmods.pre,echo=FALSE,results=hide>>=
png("graphics/tenmods.png", 600, 400)
@ 
<<tenmods>>=
images(list(data[[1]]), strip=FALSE, xlab="", ylab="")
@ 
<<tenmods.post,echo=FALSE,results=hide>>=
dev.off()
@

@@

Finally, let us take a look at some of the other modules, that were
also kept after the robustness-based filtering. Here we plot five of
them, together with the input matrix.
<<othermods.pre,echo=FALSE,results=hide>>=
png("graphics/othermods.png", 400, 400)
@ 
<<othermods>>=
othermods <- order(modules3$seeddata$rob)[1:5]
print(plotModules(modules3, othermods, data=data[[1]]))
@ 
<<othermods.post,echo=FALSE,results=hide>>=
dev.off()
@

@@

The \Rfunction{drawHeatmap} function of the \Rpackage{biclust} package
can be also used to draw an image plot. This visualizes a single
bicluster on top of the input matrix. It reorders the rows and columns
of the input matrix to move the block of the bicluster to the top
left corner of the input matrix (Fig.~\ref{fig:heatmap}).
<<drawHeatmap.pre,echo=FALSE,results=hide>>=
png("graphics/drawheatmap.png", 400,400)
@ 
<<drawHeatmap>>=
drawHeatmap(five.mods[[1]], Bc, number=1,local=FALSE)
@ 
<<drawHeatmap.post,echo=FALSE,results=hide>>=
dev.off()
@ 
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{drawheatmap}
\caption{Heatmap plot of the reordered input matrix. The rows and
  columns corresponding to the first bicluster are moved to the
  top-left corner of the matrix.}
\label{fig:heatmap}
\end{figure}

@@

<<noiseplot.pre,echo=FALSE,results=hide>>=
png("graphics/noise.png", width=800, height=600)
@ 
<<noiseplot>>=
images(lapply(data, "[[", 1), names=as.character(noise), 
       xlab="", ylab="")
@ 
<<noiseplot.post,echo=FALSE,results=hide>>=
dev.off()
@ 
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{noise}
  \caption{Modular data sets with different levels of noise. The data
  sets are generated by adding normally distributed background noise
  with given variance to the checkerboard matrix.}
  \label{fig:noise}
\end{figure}

@@

<<overlapplot.pre,echo=FALSE,results=hide>>=
png("graphics/overlapplot.png", 800, 600)
@ 
<<overlapplot>>=
plotModules(data=two.over[[1]],
            list(rows=cbind(ov.modules.1$rows, ov.modules.2$rows),
                 columns=cbind(ov.modules.1$columns,
                   ov.modules.2$column)),
            names=c("Input matrix", paste("Module", 1:6)))
@
<<overlapplot.post,echo=FALSE,results=hide>>=
dev.off()
@

@@

<<sessioninfo,results=tex,echo=FALSE>>=
toLatex(sessionInfo())
@
